---
title: "Assignment_7"
author: "Camryn Yoder"
date: "2026-10-06"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_download: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r assignment7}
# Check robots.txt first
robotstxt::paths_allowed(paths = "/fsb/directory", domain = "miamioh.edu", bot = "*")

# Department names 
dept_names = c("Accountancy", "Economics", "Entrepreneurship", "Finance", "Information Systems and Analytics", "Marketing", "Management")

# Takes one department name, returns a data frame for that department
scrape_fsb_dept = function(dept){dept_url = paste0("https://miamioh.edu/fsb/directory/?up=/query/all/all/",URLencode(dept), "/all")   # URLencode() turns spaces into %20 (had to use chatISA for help)
  
  webpage = rvest::read_html(dept_url)
  
   # Name: inside <strong> in each table cell
  webpage |>
    rvest::html_elements("td strong a") |>
    rvest::html_text2() |>
    stringr::str_remove("(Faculty|Staff)sfx.*") -> names
  
  # Website: the href attribute of that same link
  webpage |>
    rvest::html_elements("td strong a") |>
    rvest::html_attr("href") -> websites
  
  # Position: italic text under each name
  webpage |>
    rvest::html_elements("td i") |>
    rvest::html_text2() |>
    stringr::str_squish() -> positions

df = data.frame(department = dept, name = names, position = positions, website = websites)
return(df)
}

# Apply function to all departments
fsb_directory = purrr::map_df(.x = dept_names, .f = scrape_fsb_dept)

head(fsb_directory)
