---
title: "Class 11"
author: "Camryn Yoder"
date: "2026-09-30"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_download: true
    code_folding: show
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## objectives
- Scrape multipe webpages from the same website using a 'for' loop
- Scrape multiple webpages from the same website using the 'purrr' package
*Note:* In this process we will create our own function

# Re-examining Miami U bulletin example

Expanding on example from last class to include accounting
[ACC](https://bulletin.miamioh.edu/courses-instruction/acc/)
[BUS](https://bulletin.miamioh.edu/courses-instruction/bus/)
[ISA](https://bulletin.miamioh.edu/courses-instruction/isa/)
[MKT](https://bulletin.miamioh.edu/courses-instruction/mkt/)

You can repeat the code a few times with changing the URL, it will work for a few links but would be tedious for a large list of scraping.We follow the **DRY principle**: *Do not Repeat Yourself.*

```{r bulletin}
dept_abbrv= c('acc','bus','isa','mkt')

courses_df=data.frame() #initializing a container to store stuff in from the loop

for (abbrv in dept_abbrv) {
  cat( rep("-", 50), "\n")
  print(abbrv)
  bulletin_url=paste0('https://bulletin.miamioh.edu/courses-instruction/', abbrv, '/')
  
  #Store URL as an object to reuse the rest of the code only changing the URL
  webpage = rvest::read_html(bulletin_url)
  
  webpage |> 
    rvest::html_elements("strong") |> 
    rvest::html_text2() -> titles   #'cleans' the HTML text
  
  webpage |>
    rvest::html_elements("p.courseblockdesc") |>
    rvest::html_text2() -> descs
  
  df=data.frame(title=titles, desc=descs)
  courses_df=rbind(courses_df,df)
}
```


# Using purrr package

Functional programming approach and we will write our own function - called `function` as opposed to `def` in Python. In R, the functions return a single object.
```{r purrr}

dept_abbrv= c('acc','bus','isa','mkt')

#This function takes an abbrv as an input and returns a data frame as the output
scrape_mu_bulletin = function(abbrv){
    bulletin_url=paste0('https://bulletin.miamioh.edu/courses-instruction/', abbrv, '/')
  
  #Store URL as an object to reuse the rest of the code only changing the URL
  webpage = rvest::read_html(bulletin_url)
  
  webpage |> 
    rvest::html_elements("p.courseblocktitle") |> 
    rvest::html_text2() -> titles   #'cleans' the HTML text
  
  webpage |>
    rvest::html_elements("p.courseblockdesc") |>
    rvest::html_text2() -> descs
  
  df=data.frame(title=titles, desc=descs)
  return(df)
}

test = scrape_mu_bulletin(abbrv = 'eco')

#to use functions from purrr we will use a map_*() or a map2_*() or a pmap_*()
#map uses a function that takes a single input
#map2 uses a function that takes 2 inputs
#pmap takes >=3
#after the _, you put the type of object you are getting back

#the .x is the vector we will iterate over and the .f is the fuction we use
courses_df_from_purrr = purrr::map_df(.x=dept_abbrv, .f=scrape_mu_bulletin)
```



## Scrape data from the website planecrashinfo

The website we want to scrape: <https://www.planecrashinfo.com/> contains a database of plane crashes by year
```{r}
year = 2025

crash_url=paste0('https://www.planecrashinfo.com/', year, '/', year, '.htm')

crash_page=rvest::read_html(crash_url)
```

