---
title: "Class 6"
author: "Camryn Yoder"
date: "2026-09-14"
output: 
  html_document:
  toc: TRUE
  toc_float: TRUE
  code_download: TRUE
  number_sections: TRUE
  code_folding: show

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Kahoot
```{r kahoot}
run = readr::read_csv(
  "https://isa401-find-your-seat.vercel.app/api/export?section=A&run=13")
dplyr::glimpse(run)

```

Notes from Kahoot:
- A vector is a container where every element must be the same type. A list is a container where every element can be a different type, like other lists, or data frames.

- read_excel() needs a file on disk, so we downloaded in browser and NOT read its web address

- read_excel(.............. skip=1) means to skip title row above header

- [] gives back the thing itself, can only 'request' 1 at a time
  - [[]] gives a list
  
- fromJSON() is better than read_json()
  - read_csv() is better than read.csv
  
- dttm data type: short for daytime -> date and time


# HW 04
```{r hw04}
con = DBI::dbConnect(RSQLite::SQLite(), "../data/midwest_airbnb.db")
listings = DBI::dbReadTable(con, "listings")
```


# Class 6
```{r reading_data}
con = DBI::dbConnect(RSQLite::SQLite(),
                     "../data/scout.db")
DBI::dbListTables(con)
postings = DBI::dbReadTable(con, "scout_postings")
DBI::dbDisconnect(con)
dplyr::glimpse(postings[, c("title", "company",
  "location_state", "remote", "skills_json")]) #takes all rows ([,c...]) and combines hose 5 columns into 1 vector

#package::function()

```


# Ask the database a question in SQL
```{r ask_question_in_SQL}
con = DBI::dbConnect(RSQLite::SQLite(),
                     "../data/scout.db") #connection
top_remote = DBI::dbGetQuery(con, "
  SELECT company, COUNT(*) AS n
  FROM scout_postings
  WHERE remote = 1
  GROUP BY company
  ORDER BY n DESC
  LIMIT 10") #SQL query
DBI::dbDisconnect(con)
top_remote

#dbReadTable() is SELECT * FROM scout_postings with no filter.
```


# JSON inside a cell
```{r}
first_cell = postings$skills_json[1]
cat(strtrim(first_cell, 60))   # base R: first 60 characters

skills = jsonlite::fromJSON(first_cell)
skills

# postings$skills_json[1] is vector, then element; fromJSON() then turns text into structure.
```


# Part 2: First App

```{r first_app}

# apps/job_scout_chat/app.R
library(querychat)

con = DBI::dbConnect(RSQLite::SQLite(), "data/scout.db")

client = ellmer::chat_openai(
  model  = "gpt-5.6-luna",
  params = ellmer::params(reasoning_effort = "none")
)


qc = querychat(
  con, "scout_postings",
  client   = client,
  tools    = c("filter", "query", "visualize"),
  greeting = "Ask me about the 1,891 job postings
              ChatISA Job Scout collected."
)

qc$app_obj()
```


