---
title: "Class 8"
author: "Camryn Yoder"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: show
    code_download: true
date: "2026-09-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#API: application programming interface
#Which requests you may send, how to write them, and what comes back. Written for programs, not for people clicking.


#left_join() keeps the left table whole and adds the right table's columns. Where no partner exists, the new cells are NA, which is a fact worth knowing, not an error.

#Joins in practice
```{r}
states = tibble::tibble(location_state = state.abb,
                        state_name = state.name,
                        region = as.character(state.region))
jobs |>
  dplyr::left_join(states, by = "location_state") |>
  dplyr::group_by(region) |>
  dplyr::summarize(postings = dplyr::n(), remote_share = mean(remote)) |>
  dplyr::arrange(dplyr::desc(postings))
```



#AirBNB practice
```{r}
con = DBI::dbConnect(RSQLite::SQLite(), "../data/midwest_airbnb.db")
listings = DBI::dbReadTable(con, "listings") |>
  tibble::as_tibble()
DBI::dbDisconnect(con)
dplyr::glimpse(listings)

#Listings per city
#I can group by city and count number of listings in each

listings |> dplyr::group_by(city) |> dplyr::summarise(count=dplyr::n()) 

#The shortcut for the code above 

listings |> dplyr::count(city) #count does group by and then n ()

#another option is to count number of times each city occurred in the city column

table(listings$city) #returns a named vector vs above is a data frame

#For entire homes (room_type == "Entire home/apt") that sleep four or more, what is the median price in each city?

listings |> 
  dplyr::filter(room_type=="Entire home/apt", accommodates>=4
  ) |>
  dplyr::group_by(city) |>
  dplyr::summarise(
    median_price=median(price)
  )

#Which 3 listings are the cheapest per person
#for the sake of printing nicely, reduce # of columns

listings |>
  dplyr::mutate(price_per_person=price/accommodates) |>
  dplyr::select(city, host_name, name, accommodates, price_per_person) |>
  dplyr::arrange(price_per_person)


#What 5 host names have most listings, host names are not unique but host ids are

listings|>
  dplyr::count(host_name, sort=T)


#groups by both host name and host id to try to find unique host
listings|>
  dplyr::count(host_name, host_id, sort=T)
```


#API step-by-step
```{r}
httr2::request("https://data.cincinnati-oh.gov/resource/rvmt-pkmq.json") |> #Specifies request to get data from that link
  httr2::req_url_query("$limit" = 5) |> #Reconstructs URL for limit=5
  httr2::req_perform() |> #Executing request
  httr2::resp_body_string() |> #Response in a data frame
  jsonlite::fromJSON() -> cincy_crashes
```

#STATUS CODES
#200: OK
#400: Bad request
#404: Not found
#401/403: Unauthorized
#429: Too many requests
#500: Server error


#Fred API key
```{r}
httr2::request("https://api.stlouisfed.org/fred/series/observations") |>
  httr2::req_url_query(
    series_id = "IHLIDXUSOH",
    api_key = Sys.getenv("FRED_API_KEY"),
    file_type = "json"
  ) |>
  # nothing has been sent yet
  httr2::req_perform() |>
  httr2::resp_body_string() |>
  jsonlite::fromJSON() -> ohio_jobs

jobs_df=ohio_jobs[[13]]

#to get data from september 1 2026

#a: get all data and then filter rows i want
dplyr::glimpse(jobs_df)
jobs_df |> 
  dplyr::mutate(
    date = lubridate::ymd(date)
  ) |> 
  dplyr::filter(date >= '2026-09-01') -> jobs_df_mod

#rewrote date column as a date, it was character before


#b: use API since it had observation_start
httr2::request("https://api.stlouisfed.org/fred/series/observations") |>
  httr2::req_url_query(
    series_id = "IHLIDXUSOH",
    api_key = Sys.getenv("FRED_API_KEY"),
    file_type = "json",
    observation_start="2026-09-01"
  ) |>
  httr2::req_perform() |>
  httr2::resp_body_string() |>
  jsonlite::fromJSON() -> ohio_jobs_sep_2026

ohio_jobs_sep_2026_df=ohio_jobs_sep_2026$observations #saves the observations as a data frame
```


#USA Jobs API
```{r}
httr2::request("https://data.usajobs.gov/api/search") |>
  httr2::req_url_query(Keyword = "Data Analyst", ResultsPerPage = 500) |>
  httr2::req_headers(
    Host = "data.usajobs.gov",
    "User-Agent" = "yodercn@miamioh.edu",
    "Authorization-Key" = Sys.getenv("USAJOBS_API_KEY")
  ) |>
  httr2::req_perform() |>
  httr2::resp_body_string() |>
  jsonlite::fromJSON(flatten = TRUE) -> usa_jobs_list

usa_df = usa_jobs_list$SearchResult$SearchResultItems

jobs_small = usa_df |>
  dplyr::select(
    title = MatchedObjectDescriptor.PositionTitle,
    department = MatchedObjectDescriptor.DepartmentName,
    agency = MatchedObjectDescriptor.OrganizationName,
    location = MatchedObjectDescriptor.PositionLocationDisplay,
    closes = MatchedObjectDescriptor.ApplicationCloseDate
  )
```

1. How many federal postings match "Data Analyst" today?
2. Which three departments have the most of them?
```{r}

table(jobs_small$department) |> sort(decreasing=T) |> head(3)

index_data_analyst = jobs_small$title |> 
  stringr::str_detect(pattern = 'Data Analyst|Data Analytics')

jobs = jobs_small[index_data_analyst, ]
table(jobs$department)

```

